Thickness optimization in wide range quasi omnidirectional 1-D photonic structures

### 2020-12-07 PaperVictor.tex
Agregue un espacio para hacer pruebas
En PaperVictor.tex aplique el comando dos2unix, actualice a mi última versión, modifique PC a PhC  y quite una referencia duplicada. En Bibliografia.bib quite la referencia duplicada (Bruggeman2006 y Pap2006) y corregí el nombre de los compuestos involucrados en las referencias (i. e., zno a ZnO)

%\title{Thickness optimization in wide range quasi omnidirectional multilayer
% structures}
\title{ Thickness optimization in wide range quasi
omnidirectional 1-D photonic structures}
\author[1,2,3]{Victor Castillo-Gallardo\thanks{email: {\tt
			victor1\_1@hotmail.com}}}
\author[1,2,3]{Luis Eduardo Puente-Dìaz}
\author[4]{D. Ariza-Flores}
\author[3]{Hector Pérez-Aguilar}
\author[2]{W. Luis Mochán\thanks{email: {\tt
			mochan@fis.unam.mx}}}
\author[1]{Vivechana Agarwal\thanks{email: {\tt
			vagarwal@uaem.mx}}}
\affil[1]{Centro de Investigación en Ingenierìa y Ciencias Aplicadas,
	Universidad del Estado de Morelos, Av. Universidad 1001
	Col. Chamilpa, Cuernavaca, Morelos 62209, México.}
\affil[2]{Instituto de Ciencias Fìsicas, Universidad Nacional Autónoma
	de México, Av. Universidad S/N, Col. Chamilpa, 62210 Cuernavaca,
	Morelos, México.}
\affil[3]{Facultad de Ciencias Fìsico Matemáticas,
	Universidad Michoacana de San Nicolás de Hidalgo, Av. Francisco
	J. Múgica S/N 58030, Morelia, Mich., México.}
\affil[4]{Conacyt-Universidad Autónoma de San Luis Potosì, Karakorum 1470, Lomas 4ta Secc, San Luis Potosì, S.L.P., 78210, México.}
%\date{{\small {\today}}}
\maketitle

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. We
maximize the reflectance ($\braket{R}$ \notaL{El promedio no depende
  de lambda ni theta, y prom es castellano} averaged over a wide wavelength
and angular range  of PS-based mirrors with different
porosity contrasts searching for a minimum thickness. Optimization is
performed in the visible (Vis) and near infrarred (NIR) regions of the
electromagnetic spectrum. We design the mirrors using \textit{chirped}
structures and \textit{stacking} sub-mirrors. The
chirped structures were better suited for the Vis, and the stacked
sub-mirrors for the NIR regions. We design, fabricate and test some
optimized omnidirectional structures with less than 100
periods.
\end{abstract}

@@

Photonic crystal (PC)-based structures are extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation will be limited by photonic band gaps (PBGs)
where transmission states are forbidden. The PC  shows a
PBG corresponding to the electromagnetic modes which are not allowed to propagate
through the structure and behaves as a perfect mirror for that range. The width of
reflection spectrum is important while designing an omnidirectional mirror for
different applications. The metallic mirrors are widely accepted for reflection
purposes, but widespread use is limited due to their absorptive nature at the
visible and near infrared frequencies.  A good alternative are dielectric
structures as they also provide design flexibility in terms of
reflection wavelength. These properties are widely used to design various
one-dimensional (1D) and two-dimensional (2D) PCs for its
potential applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D PC is composed of alternating high $\left(
n_{H}\right) $ and low $\left(n_{L}\right) $ refractive index layers (Bragg Mirror,
BM). The optical thicknesses are typically chosen to be quarter-wavelength length, $
n_{H}d_{H}=n_{L}d_{L}=\lambda _{0}/4$, at some operating wavelength $\lambda
_{0}$ (center wavelength) to obtain a certain
omnidirectional band gap. As the gap depends on the contrast of the
refractive indices and the number of periods,  broadband mirrors can  be
engineered by modulating the reflection in a broader wavelength range.
One of the ways to obtain such structures has been the continuous variation of
thicknesses along the depth, defined as \textit{chirped}-type \cite{Zipock1997}
structures. Additionally, broader mirrors can also be achieved by overlapping
different BMs, where each one reflects around a specific central wavelength,
resulting in a wider photonic band gap \cite{Xifre2009}.

Till now, different deposition techniques have been used to obtain omnidirectional
BM (ODBM) that operate on the visible and near infrared (Vis-NIR) range of the
electromagnetic spectrum. For example, Chen et al., \cite{Chen1999} have
reported an ODBM of about 70 nm in NIR range designed with 6-pairs  of
TiO$_{2}$/SiO$_{2}$ deposited using sol-gel method. Park et al., \cite{Park2003}
used molecular beam epitaxy to grow a stack of four pairs of GaAs$/$AlAs layers,
followed by its conversion to a multilayer stack of GaAs/Al$_{2}$O$_{3}$ by selective
oxidation of the AlAs layers, to obtain an ODBM with a gap from 710 to 950
nm. On the other hand, DeCorby et al., \cite{DeCorby2005} fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain 150 nm wide omnidirectional band, centered at 1750 nm
wavelength. Furthermore, Jena et al., \cite{Jena2019}
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate 1DPC of TiO$_{2}$/SiO$_{2}$ and achieved ODBM from
592 to 668 nm. However, these techniques are expensive and
require sophisticated equipment and long fabrication time. Using porous silicon (PS)
is an alternative, as PS is typically fabricated by simple electrochemical etching of
crystalline Si in hydrofluoric acid based electrolyte, to obtain the
sponge-like nanostructure composed of Si and air in a relatively short duration of
time. The generated porosity can be tuned by changing the applied current
density and hence modifies the refractive index of the resulting PS. This
fact opens the possibility of designing 1DPC with PS, which seeks to
control the propagation of light in a dielectric medium. The low cost and
ease of obtaining porous silicon make it an excellent candidate to develop
optical devices based on multilayer structures \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of porous silicon, they have been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
photoluminescence control \cite{Antunez2014}. Recently, the study of
quasi-omnidirectional Bragg mirrors has increased due to their possible application
as a flat lens \cite{Kozar2017,Cheng2018}. In particular, PS based dielectric
optical filters, quasi-ODBM and ODBM have been extensively studied in different
regions of the electromagnetic spectrum, such as ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR) \cite{Bruyant2003}. Keeping
in view that high values of average porosity, refractive index contrast and
thickness make the multilayer structures fragile, in this work various wide
band gap photonic structures have been proposed to obtain maximal average
reflectance (R$_{\text{ave}}\left( \lambda ,\theta \right) $) with the minimum
possible thickness and low refractive index contrast.

@@

In the analysis of the propagation of the electromagnetic field through
multilayer systems, it is common to employ the transfer matrix method (put the
reference). Under the consideration that the system only varies along the $z$ axis, the transfer matrix is $M\left(z_{2},z_{1}\right)$
a 2x2 matrix that relates the components of the electric field E$_{\parallel }$
and the magnetic field H$_{\parallel }$ parallel to the $xy$ plane, and
normal to the axis of the structure, evaluated at any two points $z_{2}$
and $z_{1}$
\begin{equation*}
\left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain $M$ \cite%
{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
to calculate the reflectance of large multilayer systems proposed by Puente-D%
\'{\i}az, et al \cite{Puente2020}, since we need a reliable and stable tool
to design an optimized structure through a minimization procedure that
requires the calculation of complete spectra for all sets of design parameters.
The development of $M$ is shown in the supplementary information. Therefore, the
explicit expressions for the optical coefficients are:
\begin{equation}
r=\mp \frac{Z_{0}\tilde{M}_{11}+\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}_{21}-Z_{s}%
\tilde{M}_{22}}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
_{21}+Z_{s}\tilde{M}_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha }}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
_{21}+Z_{s}\tilde{M}_{22}},  \label{tBloch}
\end{equation}%
where the upper sign $-$ in Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization, respectively. Furthermore, $\tilde{M}_{ij}$ are the elements of the transfer matrix. As usual, the reflectance is given by $R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=Z_{0}/Z_{s}$ for the case of TE polarization and $\beta =Z_{s}/Z_{0}$ for
the case of TM polarization. Additionally, complex refractive indices of the porous
layers in the simulations were obtained by Bruggeman effective medium theory, which
has been reported to adequately reproduce the PS optical parameters
\cite{Giusseppe2011,Pap2006,Estrada2018}.

@@

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, p-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. Electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous HF (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
With this electrolyte, the minimum and maximum porosities that can be
obtained are 35$\%$ and 76$\%$ (gravimetrically obtained), using current densities of 0.5 and 305 mA$/$%
cm$^{2}$, respectively. However, it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte diffusivity problems \cite{Ariza2011}.
For this reason, the current
densities were chosen as 35 and 305 mA$/$cm$^{2}$, with corresponding
porosities of 51$\%$ and 76$\%$, respectively. The calibration curves were
acquired through a gravimetric technique as follows: single layers of porous
silicon were synthesized under similar conditions and were weighed ($m_{i}$)
before ($m_{1}$) and after ($m_{2}$) the electrochemical attack, and after
dissolving the already formed porous silicon layer ($m_{3}$), to calculate
the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Brugeman2006}. Etching
rate of PS was obtained by re-synthetizing individual layers under similar
conditions and measuring their thicknesses through scanning electron
microscopy (SEM). The absolute reflectivity measurements were carried out
with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
angle universal reflectance accessory (URA) for different incident angles $%
\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $%
50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
minimum values of $\theta _{i}$ were constrained by the angular range of the
equipment accessory URA.

@@

This section presents the comparison of the calculated and measured reflectance
spectra at different incidence angles in the regions of interest. In the first
subsection, the design and optimization of R$_{\text{ave}}
\left(\lambda,\theta\right)$ of \textit{chirped}  photonic structures is presented,
and next subsection the design of the structure is analyzed through sub-mirrors
stacks.

@@

The generic form of the expression that modulates the design of photonic
structure is:
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left( x_{j}\right),\label{Dis}
\end{equation}%
where $\lambda _{\min }$, $\lambda _{\max }$ and $\lambda _{j}$ correspond
to the minimum, maximum, and design wavelengths to which the $j$-th period
is tuned, respectively, and $f\left( x_{j}\right) $ represents any
normalized function that modulates the thickness. Here $x_{j}=\frac{j}{N_{p}}$ being
$j$ the $j$-th period and $N_{p}$ the total number of periods that the structure
will contain. Only restriction for $f\left( x_{j}\right) $ is that it has to be an
increasing function, due to the high absorption of PS in the ultraviolet region
which decreases in the visible and becomes negligible in the near infrared. So, the
first periods are syntonized in the UV-Vis regions. This work shows the analysis
of following functions:
\begin{equation}
f_{1}\left( x\right) =x^{\alpha },  \label{F1}
\end{equation}%
\begin{equation}
f_{2}\left( x\right) =A\left( x^{\alpha }+x^{\beta}\right)
\label{F2}
\end{equation}%
and%
\begin{equation}
f_{3}\left( x\right) =Ax^{\alpha }\left( 1-x\right) +x^{\beta },  \label{F3}
\end{equation}%
where $\alpha $, $\beta $ and $A$ are parameters to optimize. The function
$f_{1}$ (Eq. (\ref {F1})) represents the simplest profiles. The restrictions
for the values $\alpha$ are that they must be positive and they must not be
extremely large or small. In these cases, mirrors that reflect in $\lambda _{\text{min}}$ or $\lambda _{\text{max}}$,
respectively, will be obtained. Eq. (\ref{F2}) is formed by the average of
two functions of type $f_{1}$ with different powers. The function $f_{3}$
(Eq. (\ref{F3})) was designed so that the first and second additions
predominate the short and long wavelengths, respectively. The R$_{\text{ave}}
\left(\lambda,\theta\right)$ of the structures is calculated in
the wavelength range from 350 to 1400 nm and from 0 to 90${{}^\circ}$ angle of
incidence. The optimized parameters using a porosity contrast of $51/76\%$ are shown
in Table 1 and in the supplementary information they appear for the porosity
contrasts of $30/76\%$ and $42/76\%$.
\begin{table}
\caption{ Design parameters obtained after the optimization of functions (Eqs. (\ref{F1}) - (\ref{F3})) for maximum average reflectance and minimum thickness }%
\includegraphics[width=\textwidth]
{F2TableOptimized.pdf}
\end{table}

>>>>

%\title{Thickness optimization in wide range quasi omnidirectional multilayer
% structures}
\title{ Thickness optimization in wide range quasi
omnidirectional 1-D photonic structures}
\author[1,2,3]{Victor Castillo-Gallardo\thanks{email: {\tt
			victor1\_1@hotmail.com}}}
\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
\author[4]{D. Ariza-Flores}
\author[3]{Hector P\'{e}rez-Aguilar}
\author[2]{W. Luis Moch\'{a}n\thanks{email: {\tt
			mochan@fis.unam.mx}}}
\author[1]{Vivechana Agarwal\thanks{email: {\tt
			vagarwal@uaem.mx}}}
\affil[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y 
Ciencias Aplicadas, Universidad del Estado de Morelos, Av. 
Universidad 1001, Col. Chamilpa, Cuernavaca, Morelos 62209, 
M\'{e}xico.}
\affil[2]{Instituto de Ciencias F\'{i}sicas, Universidad 
Nacional Aut\'{o}noma de M\'{e}xico, Av. Universidad S/N, 
Col. Chamilpa, 62210 Cuernavaca, Morelos, México.}
\affil[3]{Facultad de Ciencias Fìsico Matem\'{a}ticas, 
Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av. 
Francisco J. Múgica S/N 58030, Morelia, Mich., M\'{e}xico.}
\affil[4]{CONACyT-Universidad Aut\'{o}noma de San Luis 
Potosì, Karakorum 1470, Lomas 4ta Secc, San Luis Potos\'{i}, 
S.L.P., 78210, M\'{e}xico.}
%\date{{\small {\today}}}
\maketitle

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. We
maximize the reflectance ($\braket{R_{\text{ave}}}$ \notaL{El promedio no depende
  de lambda ni theta, y prom es castellano} averaged over a wide wavelength
and angular range  of PS-based mirrors with different
porosity contrasts searching for a minimum thickness. Optimization is
performed in the visible (Vis) and near infrarred (NIR) regions of the
electromagnetic spectrum. We design the mirrors using \textit{chirped}-type
structures and \textit{stacking} sub-mirrors. The
chirped structures were better suited for the Vis, and the stacked
sub-mirrors for the NIR regions. We design, fabricate and test some
optimized omnidirectional structures with less than 100
periods.
\end{abstract}

@@

Photonic crystal (PhC)-based structures are extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation will be limited by photonic band gaps (PBGs)
where transmission states are forbidden. The PhC  shows a
PBG corresponding to the electromagnetic modes which are not allowed to propagate
through the structure and behaves as a perfect mirror for that range. The width of
reflection spectrum is important while designing an omnidirectional mirror for
different applications. The metallic mirrors are widely accepted for reflection
purposes, but widespread use is limited due to their absorptive nature at the
visible and near infrared frequencies.  A good alternative are dielectric
structures as they also provide design flexibility in terms of
reflection wavelength. These properties are widely used to design various
one-dimensional (1D) and two-dimensional (2D) PhCs for its
potential applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1DPhC is composed of alternating high $\left(
n_{H}\right) $ and low $\left(n_{L}\right) $ refractive index layers (Bragg Mirror,
BM). The optical thicknesses are typically chosen to be quarter-wavelength length, $
n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$, at some operating wavelength $\lambda_{0}$ 
(center wavelength) to obtain a certain
omnidirectional band gap. As the gap depends on the contrast of the
refractive indices and the number of periods,  broadband mirrors can  be
engineered by modulating the reflection in a broader wavelength range.
One of the ways to obtain such structures has been the continuous variation of
thicknesses along the depth, defined as \textit{chirped}-type \cite{Zipock1997}
structures. Additionally, broader mirrors can also be achieved by overlapping
different BMs, where each one reflects around a specific central wavelength,
resulting in a wider photonic band gap \cite{Xifre2009}.

Till now, different deposition techniques have been used to obtain omnidirectional
BM (ODBM) that operate on the visible and near infrared (Vis-NIR) range of the
electromagnetic spectrum. For example, Chen et al., \cite{Chen1999} have
reported an ODBM of about 70 nm in NIR range designed with 6-pairs  of
TiO$_{2}$/SiO$_{2}$ deposited using sol-gel method. Park et al., \cite{Park2003}
used molecular beam epitaxy to grow a stack of four pairs of GaAs$/$AlAs layers,
followed by its conversion to a multilayer stack of GaAs/Al$_{2}$O$_{3}$ by selective
oxidation of the AlAs layers, to obtain an ODBM with a gap from 710 to 950
nm. On the other hand, DeCorby et al., \cite{DeCorby2005} fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain 150 nm wide omnidirectional band, centered at 1750 nm
wavelength. Furthermore, Jena et al., \cite{Jena2019}
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate 1DPhC of TiO$_{2}$/SiO$_{2}$ and achieved ODBM from
592 to 668 nm. However, these techniques are expensive and
require sophisticated equipment and long fabrication time. Using PS
is an alternative, as PS is typically fabricated by simple electrochemical etching of
crystalline Si in hydrofluoric acid based electrolyte, to obtain the
sponge-like nanostructure composed of Si and air in a relatively short duration of
time. The generated porosity can be tuned by changing the applied current
density and hence modifies the refractive index of the resulting PS. This
fact opens the possibility of designing 1DPhC with PS, which seeks to
control the propagation of light in a dielectric medium. The low cost and
ease of obtaining porous silicon make it an excellent candidate to develop
optical devices based on multilayer structures \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common 
application of porous silicon, they have been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
photoluminescence control \cite{Antunez2014}. Recently, the study of
quasi-omnidirectional Bragg mirrors has increased due to their possible application
as a flat lens \cite{Kozar2017,Cheng2018}. In particular, PS based dielectric
optical filters, quasi-ODBM and ODBM have been extensively studied in different
regions of the electromagnetic spectrum, such as ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR) \cite{Bruyant2003}. Keeping
in view that high values of average porosity, refractive index contrast and
thickness make the multilayer structures fragile, in this work various wide
band gap photonic structures have been proposed to obtain maximal average
reflectance (R$_{\text{ave}}\left( \lambda ,\theta \right) $) with the minimum
possible thickness and low refractive index contrast.

@@

In the analysis of the propagation of the electromagnetic field through
multilayer systems, it is common to employ the transfer matrix method (put the
reference). Under the consideration that the system only varies along the $z$ axis, the 
transfer matrix is $M\left(z_{2},z_{1}\right)$
a 2x2 matrix that relates the components of the electric field E$_{\parallel }$
and the magnetic field H$_{\parallel }$ parallel to the $xy$ plane, and
normal to the axis of the structure, evaluated at any two points $z_{2}$
and $z_{1}$
\begin{equation*}
\left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain $M$ 
\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
to calculate the reflectance of large multilayer systems proposed by Puente-D%
\'{\i}az, et al. \cite{Puente2020}, since we need a reliable and stable tool
to design an optimized structure through a minimization procedure that
requires the calculation of complete spectra for all sets of design parameters.
The development of $M$ is shown in the supplementary information. Therefore, the
explicit expressions for the optical coefficients are:
\begin{equation}
r=\mp \frac{Z_{0}\tilde{M}_{11}+\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}_{21}-Z_{s}%
\tilde{M}_{22}}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
_{21}+Z_{s}\tilde{M}_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha }}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
_{21}+Z_{s}\tilde{M}_{22}},  \label{tBloch}
\end{equation}%
where the upper sign $-$ in Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization, respectively. Furthermore, $\tilde{M}_{ij}$ are the elements of the transfer matrix. As usual, the reflectance is given by $R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=Z_{0}/Z_{s}$ for the case of TE polarization and $\beta =Z_{s}/Z_{0}$ for
the case of TM polarization. Additionally, complex refractive indices of the porous
layers in the simulations were obtained by Bruggeman effective medium theory, which
has been reported to adequately reproduce the PS optical parameters
\cite{Giusseppe2011,Pap2006,Estrada2018}.

@@

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, p-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. Electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous HF (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
With this electrolyte, the minimum and maximum porosities that can be
obtained are 35$\%$ and 76$\%$ (gravimetrically obtained), using current densities of 0.5 and 305 mA$/$%
cm$^{2}$, respectively. However, it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte diffusivity problems \cite{Ariza2011}.
For this reason, the current
densities were chosen as 35 and 305 mA$/$cm$^{2}$, with corresponding
porosities of 51$\%$ and 76$\%$, respectively. The calibration curves were
acquired through a gravimetric technique as follows: single layers of porous
silicon were synthesized under similar conditions and were weighed ($m_{i}$)
before ($m_{1}$) and after ($m_{2}$) the electrochemical attack, and after
dissolving the already formed porous silicon layer ($m_{3}$), to calculate
the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Pap2006}. Etching
rate of PS was obtained by re-synthetizing individual layers under similar
conditions and measuring their thicknesses through SEM (Scanning Electron
Microscopy). The absolute reflectivity measurements were carried out
with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
angle universal reflectance accessory (URA) for different incident angles $%
\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $%
50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
minimum values of $\theta _{i}$ were constrained by the angular range of the
equipment accessory URA.

@@

This section presents the comparison of the calculated and measured reflectance
spectra at different incidence angles in the regions of interest. In the first
subsection, the design and optimization of R$_{\text{ave}}$ of \textit{chirped}  
photonic structures is presented, and next subsection the design of the structure is 
analyzed through sub-mirrors stacks.

@@

The generic form of the expression that modulates the design of photonic
structure is:
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left( x_{j}\right),\label{Dis}
\end{equation}%
where $\lambda_{\min }$, $\lambda_{\max }$ and $\lambda_{j}$ correspond
to the minimum, maximum, and design wavelengths to which the $j$-th period
is tuned, respectively, and $f\left( x_{j}\right) $ represents any
normalized function that modulates the thickness. Here $x_{j}=\frac{j}{N_{p}}$ being
$j$ the $j$-th period and $N_{p}$ the total number of periods that the structure
will contain. Only restriction for $f\left( x_{j}\right) $ is that it has to be an
increasing function, due to the high absorption of PS in the ultraviolet region
which decreases in the visible and becomes negligible in the near infrared. So, the
first periods are syntonized in the UV-Vis regions. This work shows the analysis
of following functions:
\begin{equation}
f_{1}\left( x\right) =x^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
f_{2}\left( x\right) =A\left( x^{\alpha }+x^{\beta}\right)
\label{F2}
\end{equation}
and%
\begin{equation}
f_{3}\left( x\right) =Ax^{\alpha }\left( 1-x\right) +x^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize. The function
$f_{1}$ (Eq. (\ref {F1})) represents the simplest profiles. The restrictions
for the values $\alpha$ are that they must be positive and they must not be
extremely large or small. In these cases, mirrors that reflect in 
$\lambda_{\text{min}}$ or $\lambda _{\text{max}}$, respectively, will be obtained. Eq. 
(\ref{F2}) is formed by the average of two functions of type $f_{1}$ with different 
powers. The function $f_{3}$ (Eq. (\ref{F3})) was designed so that the first and second 
additions predominate the short and long wavelengths, respectively. The 
R$_{\text{ave}}$ of the structures is calculated in
the wavelength range from 350 to 1400 nm and from 0 to 90${{}^\circ}$ angle of
incidence. The optimized parameters using a porosity contrast of $51/76\%$ are shown
in Table 1 and in the supplementary information they appear for the porosity
contrasts of $30/76\%$ and $42/76\%$.
\begin{table}
\caption{ Design parameters obtained after the optimization of functions (Eqs. 
(\ref{F1}) - (\ref{F3})) for maximum average reflectance and minimum thickness }%
\includegraphics[width=\textwidth]
{F2TableOptimized.pdf}
\end{table}

According to the values shown in table I, the structure (named as ST-A) that has the
maximum average reflectance with the minimum thickness is the one designed
with the function $f_{3}$ (Eq. (\ref{F3})). Thus, the first and last periods
are tuned to 320 and 1400 nm, respectively. The complete distribution of the
periods is presented in Fig. \ref{Fig2}(a).
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]
{F3OptimizedVis.pdf}
\end{center}
\caption{(a) Distribution of $\protect\lambda_{j}$ in the $j$-th period for
the design of the 63-period multilayer structure. (b) Mapping of the average
reflectance of the structures designed with different values{}of $%
\protect\alpha $ and $N_{p}$ parameters. It is verified that the parameters
obtained during the optimization are adequate ($\protect\alpha =1.23$ and $%
N_{p}=63$). (c) Mapping the calculated reflectance for non polarized light of the
designed structure with the optimized values. (d) Comparison of reflectance spectra
calculated and measured at different angles of incidence. The gray band indicates the
region in which the reflectance is greater than 95\%. Inset shows the
top view photograph of the synthesized structure.}
\label{Fig2}
\end{figure}
To verify that the values obtained are optimal, in Fig. \ref{Fig2}(b), the average 
reflectances of the photonic structures designed with different parameters are mapped 
and, indeed, the values are in the area where R$_{\text{ave}}$ is maximum. Here, the 
parameters $\lambda_{\text{min}}$, $\lambda_{\text{max}}$, $\beta$ and $A$ were 
adjusted, while $N_{p}$ and $\alpha$ varied from 30 to 200 periods and from 0.4 to 1.3, 
respectively. The calculated reflectance, R$\left( \lambda ,\theta \right) $, of the 
photonic structure is shown in Fig \ref{Fig2}(c). Here, the wavelength and incidence 
angle cover the ranges from 350 to 1400 nm, and from 0${{}^\circ}$ to 90${{}^\circ}$, 
respectively. Calculations indicate that the structure has a localized omnidirectional 
band gap from 1000 to 1200 nm, taken with a reflectance greater than 95$\%$. Due to
experimental limitations, reflectance spectra for non polarized light are shown in all results. In Fig. \ref{Fig2}(d), the calculated and measured reflectance is compared
at 10${{}^\circ}$, 20${{}^\circ}$, 30${{}^\circ}$, 40${{}^\circ}$, 50${{}^\circ}$
and 60${{}^\circ}$ of incidence. In this angular range, the structure has a
quasi-omnidirectional band gap (R$\left(\lambda,\theta\right)>95\%$) located from
980 to 1340 nm. The numerical and experimental spectral line shapes at different
angles are in good agreement. For wavelengths greater than 700 nm and lying between
10${{}^\circ}$ to 40${{}^\circ}$ of incidence angle, the difference in spectra is
less than $5\%$. For angles of incidence greater than 40 degree, although their
characteristics are similar, the measured spectrum demonstrates relatively less
reflectance than calculated reflectance. This difference can be attributed, in part,
to the scattering of light between each of the actual interfaces, which generally
have some roughness \cite{Theiss1994,Chavez2020}.

Due to the absorptive nature of Si in the UV and visible region, it is relatively
difficult to design porous silicon omnidirectional mirrors in that region.
However, in the IR region, it is relatively easy to obtain highly reflective
and even omnidirectional photonic structures over a wide range. Therefore,
the average reflectance was optimized using the function $f_{1}$ (Eq. (\ref{F1}))
in the region of 850 to 3000 nm. It was found that the best value for
$\alpha $ is 1.2 and the minimum thickness is 60.4 $\mu$m, distributed in
90 periods. The complete design of the structure (named as ST-B) is graphed in Fig.
\ref{Fig3}(a).
\begin{figure}[tbph]
\begin{center}
\includegraphics[width=\textwidth]
{F4OptimizedNIRPC.pdf}
\end{center}
\caption{(a) Distribution of $\protect\lambda _{j}$ in the $j$-th period
modulated by the optimization of the function $f_{1}$ for the design of the
multilayer structure of 90 periods. (b) Mapping of the average reflectance
of the structures designed with different values of the $\protect\alpha $
and $N_{p}$ parameters. The optimized parameters are $\protect\alpha =1.2$
and 90 periods. (c) Mapping the calculated reflectance of the designed
structure with the optimized values for non polarized light. (d) Comparison of
reflectance spectra calculated and measured at different angles of incidence. The
gray band indicates the region in which the reflectance is greater than 95$\%$. Inset
there is a photograph of the synthesized structure.}
\label{Fig3}
\end{figure}

In Fig \ref{Fig3}(b) the average reflectance of structures
designed with different values of $\alpha$ and $N_{p}$ is mapped. As in the
previous case, the optimized parameters are within the zone of maximum
average reflectance. The reflectance calculation shows that this structure
has a wide quasi-omnidirectional gap that goes from 850 to 3000 nm and from
0${{}^\circ}$ to 70${{}^\circ}$ of incidence; the corresponding contour plot is
shown in Fig. \ref{Fig3}(c) and its average reflectance between $850-3000$ nm is
greater than 95\%. The measured and calculated reflectance spectra have very
similar characteristics as shown in Fig \ref{Fig3}(d).  The synthesized PS
multilayered 1D photonic structure has a quasi omnidirectional (from 0${{}^\circ}$
to 60${{}^\circ}$) band gap of approximately 1800 nm. The difference
between the calculated and measured spectra at the longer wavelengths can be
attributed to a thickness gradient along the depth, which is more pronounced in
the lower layers due to the restricted diffusivity of the electrolyte
through the structure itself \cite{Negro2003,Vincent1993} and interface roughness.
